---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# incidenceflow

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/incidenceflow)](https://cran.r-project.org/package=incidenceflow)
<!-- badges: end -->

The goal of incidenceflow is to ...

## Installation

You can install the released version of incidenceflow from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("incidenceflow")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(incidenceflow)
## basic example code
```

### incidence(cially) usefull

- `get_info_tidy`: generates a tibble of `incidence::get_info()`. [clink here for more information](https://www.repidemicsconsortium.org/incidence/index.html).
- `tidy_incidence`: generates a complete summary tibble from incidence fit paramteter estimates
- `glance_incidence`: generates a complete summary tibble from incidence fit model performance


```{r}
# packages ----------------------------------------------------------------

if(!require("devtools")) install.packages("devtools")
# if(!require("avallecam")) devtools::install_github("avallecam/avallecam") #improvements

library(tidyverse) #magrittr and purrr packages
library(lubridate) #ymd
library(outbreaks) #sample data
library(incidence) #core functions

# example outbreak --------------------------------------------------------

dat <- ebola_sim$linelist$date_of_onset
i.7 <- incidence(dat, interval=7)
# plot(i.7)
f1 <- fit(i.7[1:20])
f2 <- fit_optim_split(i.7)

# broom like functions ----------------------------------------------------

# tidy
f1 %>% tidy_incidence()
f2 %>% pluck("fit") %>% tidy_incidence()

# glance
f1 %>% glance_incidence()
f2 %>% pluck("fit") %>% glance_incidence()


# using purrr -------------------------------------------------------------

# using purrr::map family function allows easy stratification
# for gender and could be extrapolated to administrative levels
# in country level analysis

incidence_purrr <- ebola_sim$linelist %>% 
  as_tibble() %>% 
  #filter observations explicitly before incidence()
  filter(date_of_onset<lubridate::ymd(20141007)) %>% 
  #stratify by any group of covariates
  group_by(gender) %>% 
  nest() %>% 
  mutate(incidence_strata=map(.x = data,
                              .f = ~incidence(.x %>% pull(date_of_onset),
                                              interval=7))) %>% 
  mutate(strata_fit=map(.x = incidence_strata,
                            .f = fit)) %>% 
  mutate(strata_fit_tidy=map(.x = strata_fit,
                                  .f = tidy_incidence)) %>% 
  mutate(strata_fit_glance=map(.x = strata_fit,
                                       .f = glance_incidence))

# keep only the tibbles
incidence_purrr_tibble <- incidence_purrr %>% 
  select(-data,-incidence_strata,-strata_fit)

# tidy_incidence output
incidence_purrr_tibble %>% 
  unnest(cols = c(strata_fit_tidy))

# glance_incidence output
incidence_purrr_tibble %>% 
  unnest(cols = c(strata_fit_glance))
```


## A more update approach here

look at this project: https://github.com/reconhub/incidence2
